---
title: "Is Classical music boring?"
subtitle: "Taylor Swift and J.S. Bach compared"
author: "Miriam Heiss"
sidebar: true
toc: false
format:
  html:
    code-fold: show
    code-tools: false
---


Taylor Swift and Bach are compared to answer the question 'Is classical music boring?'. The data used for this project was from the **spotifyr** package, and variables like tempo, energy, and length were pulled. The scatterplots I made help visualize the many answers to that question. Most people think that Classical music is long and boring, but Taylor Swift (on average) is almost 2 minutes longer than Bach.

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(spotifyr)
library(patchwork)
library(plotly)
```

```{r variables, echo = FALSE}
ts_albums_clean <- read_rds("data/ts_albums.rds") # V
bach_audio <- read_rds("data/bach_audio.rds") # D
ts_audio_raw <- read_rds("data/ts_audio.rds") # D
ts_audio_clean <- read_rds("data/ts_clean_audio.rds") # D
bach_audio_clean <- read_rds("data/bach_clean_audio.rds") # D
```

::: {.column-page-inset}

```{r plots_length, echo = FALSE, out.width = "90%", fig.width = 9, fig.height = 6, warning = FALSE, message = FALSE}
library(tidyverse)
library(patchwork)
bach_length <- readRDS("data/bach_length_plot.rds")
ts_length<- readRDS("data/ts_length_plot.rds")
ts_length + bach_length
```

:::

The graph above shows the length of songs by Taylor Swift and Bach. As you can see, a lot of Bach's pieces are not the average [three minutes, thirty seconds](https://www.vox.com/2014/8/18/6003271/why-are-songs-3-minutes-long), most being much shorter. Taylor Swift, on the other hand is above the average length.





