---
title: "Is Classical Music Boring?"
subtitle: "Taylor Swift and J.S. Bach compared"
author: "Miriam Heiss"
sidebar: true
toc: false
format:
  html:
    code-fold: show
    code-tools: false
---

## Introduction

Taylor Swift and Bach are compared to answer the question 'Is classical music boring?'. The scatterplots below help visualize the answer to that question. The data used for this project was from the [**spotifyr**](lhttps://www.rcharlie.com/spotifyr/) package, and variables like tempo, energy, and length were pulled. Is classical music boring?

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(spotifyr)
library(patchwork)
library(plotly)
```

```{r variables, echo = FALSE}
ts_albums_clean <- read_rds("data/ts_albums.rds") # V
bach_audio <- read_rds("data/bach_audio.rds") # D
ts_audio_raw <- read_rds("data/ts_audio.rds") # D
ts_audio_clean <- read_rds("data/ts_clean_audio.rds") # D
bach_audio_clean <- read_rds("data/bach_clean_audio.rds") # D
```

::: {.column-page-inset}

```{r plots_energy, echo = FALSE, out.width = "90%", fig.width = 9, fig.height = 9}
bach_energy<- readRDS("data/bach_energy_plot.rds")
ts_energy<- readRDS("data/ts_energy_plot.rds")
ts_energy + bach_energy
```
:::

The plot above shows the energy level by key. Most of Taylor Swift's songs are above 0.50, and most of Bach's are below. The most common keys for Bach are G major, E major, B minor, and D major, while the most common keys for Taylor Swift are C major, D major, G major, D major, and F major. The most energetic albums for Taylor Swift are ***1989***, ***Speak Now***, and ***Fearless***. The least energetic albums are ***folklore*** and ***evermore***. For Bach, the most energetic albums are ***Innovations: Bach***, and ***J. S. Bach: Cantatas***. The least energetic album is ***Bach on Porthan Organ***. The correlation between the x and the y is that more major keys have higher energy. You can find the interactive plot [here](https://www.miriamheiss.com/final-project/interactive.html), that way you can see the name of the song.





