---
title: "Interactive Plots"
#date: "2022-08-04"
categories:
#image:  
sidebar: true
toc: false
format:
  html:
    code-fold: show
    code-tools: false
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(plotly)
library(patchwork)
```

## Energy
### Taylor Swift
 
The graph below shows the level of energy in Taylor Swift's songs. The most energetic albums are ***1989***, ***Speak Now***, and ***Fearless***. The least energetic albums are ***folklore*** and ***evermore***. Most songs lie between 0.50 and 0.75. She also tends to stick to major keys that are not sharp or flat, like C major, D major, F major, and G major.

::: {.callout-note}
Drag your mouse over the graphs, they show the name of the song!
You can also double click on the legend, that will isolate the album you clicked on!
You can also click on the legend to hide the albums.
:::

```{r, echo = FALSE, message = FALSE, warning = FALSE, out.width = "90%", fig.width = 9}
ts_audio_clean <- readRDS("data/ts_clean_audio.rds") # D
ts_albums_clean <- read_rds("data/ts_albums.rds") # V

ts_graph <- ggplot(data = ts_audio_clean,
       mapping = aes(x = key_mode,
                     y = energy,
                     color = album_name, 
                     text = track_name))+ 
  geom_hline(yintercept = 0.5)+
  geom_point(size = 2)+ 
  scale_color_manual(values = c("deepskyblue2",
                                "lightsalmon4",
                                "goldenrod",
                                "seashell4",
                                "palevioletred1",
                                "darkred",
                                "grey20",
                                "orchid4",
                                "palegreen4"))+
   scale_y_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.00))+
  coord_cartesian(ylim = c(0.0, 1.00))+
  labs(title = "Energy by Key (Taylor Swift)",
       y = "Energy",
       x = "Key", 
       color = "Album")+ 
  #annotate(geom = "label", x = "A#", y = 0, label = "Low")+ 
  #annotate(geom = "label", x = "A#", y = 1, label = "High")+ 
  theme_linedraw(base_size = 12)+ 
  theme(legend.position = "right", axis.text.x = element_text(angle = 90))
```

```{r, warning = FALSE, echo = FALSE}
ggplotly(ts_graph, tooltip = "text")
```


### J. S. Bach

This graph shows the energy of three albums by J. S. Bach. Most songs are under 0.50. The most energetic albums are ***Innovations: Bach***, and ***J. S. Bach: Cantatas***. The least energetic album is ***Bach on Porthan Organ***. The most common keys are G major, D major, E major, B minor, and A# major.

```{r, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
bach_audio_clean <- readRDS("data/bach_clean_audio.rds") # D
bach_audio <- readRDS("data/bach_audio.rds") # D

bach_graph <- bach_audio_clean %>%  
  ggplot(mapping = aes(x = key_mode, 
         y = energy, 
         color = album_name, 
         text = track_name))+ 
  geom_hline(yintercept = 0.5)+
  geom_point(size = 2, alpha = 0.75) + 
  scale_color_manual(values = c("#dbac00",
                                "#3e8996",
                                "#913e96",
                                "#de81a0"))+ 
  scale_y_continuous(breaks = c(0.0, 0.25, 0.50, 0.75, 1.00)) + 
  coord_cartesian(ylim = c(0.0, 1.00))+ 
  theme_linedraw(base_size = 12)+
  theme(axis.text.x = element_text(angle = 90), legend.position = "bottom")+ 
  labs(title = "Energy by Key (J. S. Bach)", 
       x = "Key", 
       y = "Energy",
       color = "Album")
```


```{r, echo = FALSE, warning = FALSE}
ggplotly(bach_graph, tooltip = "text")
```


