---
title: "Valence by Tempo"
sidebar: true
toc: false
format:
  html:
    code-fold: show
    code-tools: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
:::{.callout-tip}
## Terms you should know
- BPM
  - Beats Per Minute 
- Tempo
  - How fast the song goes
- Valence
  - The mood of the song
:::

These graphs show the correlation between tempo and valence. Bach usually stays below 175 bpm and is very happy. There is a lot of over plotting at the very top of Bach's plot, and it does not follow the curve very much. Taylor Swift does follow the curve. Her tempo and valence go up, down, up, down, following the curve, but mainly staying in the middle zone, having a somewhat happy mood. For her, there is a correlation, for Bach, there is not. They do have similarities in their points, though. Both are going on a noticeable downward curve for valence after 175 bpm.

::: {.column-page-inset}

```{r plots_valence, echo = FALSE, out.width = "90%", fig.width = 9, fig.height = 9, warning = FALSE, message = FALSE}
library(tidyverse)
library(patchwork)
bach_valence <- readRDS("data/bach_tempo_plot.rds")
ts_valence <- readRDS("data/ts_tempo_plot.rds")
ts_valence + bach_valence
```
:::