---
title: "Plotting Quadratic Equations"
subtitle: "Functions"
# date: 
categories: [math]
# image: 
format:
  html:
    code-fold: show
    code-tools: true
---

We know what a quadratic equation is:

$$
ax^2 + bx + c = 0
$$

But what if we could actually *see* the answers, plotted out in a graph?

\ 

## Some equations

Before we can plot anything, we need an equation.

We will be plotting 4 equations. Here they are:

- $x^2 - 11x + 28$
- $x^2 - x + 46$
- $x^2 + 49$
- $x^2 -4x$

## Making Functions

We need to make a function first. We will use variables f, g, h, and k for our functions. Here's how you make a function:

```{r, function-f}
f <- function(x) {
  x^2 - 11*x + 28
}
```

### What's going on here?

Let's break down each part of the function. The `function(x)` part is the number we will plug in, it is the same as writing $f(x)$. Now, what does $f(x)$ equal? That is the part that goes in the curly brackets. We also want to save it to an object `f`.

This:

```{r, function}
f <- function(x) {
  x^2 - 11*x + 28
}
```

Is the same thing as this:

$$
f(x) = x^2 - 11x + 28
$$

## All of the other functions

Here's what the rest of the functions are written in code:

``` {r, function-g-h-k}
g <- function(x) {
  x^2 - x + 46
}

h <- function(x) {
  x^2 + 49
}

k <- function(x) {
  x^2 -4*x
}
```

And here they are not in code; $g(x) = x^2 - x + 46$, $h(x) = x^2 + 49$, $k(x) = x^2 - 4x$

## Let's graph!

Now that we have all of our functions written out, we can plug any number in for $x$


```{r}
library(tidyverse)

ggplot()+
  geom_function(fun = f)
```







